Polyester RNA-seq simulation study

### 2018-02-16 datasets/RNA-Seq/polyester-replicates-benchmarkFDR.Rmd
changed log2FC sd to 1

    # randomly sample a log2FC from truncated N(0,0.5) (greater than 0.5) 
    log2FC <- rep(0, nrow(counts))
    # log2FC[DE] <- rtruncnorm(nDE, 1, sd=.5) * sample(c(1,-1), size=nDE, replace=TRUE)
    log2FC[DE] <- c(rnorm(nDE, sd = 1.5), rep(0,nrow(counts)-nDE))
    dat_alt = create_read_numbers(paramPolyester$mu, paramPolyester$fit,
                                  paramPolyester$p0, m=dim(counts)[1], 
                                  n=sampleSize*2, beta=cbind(log2FC), 
                                  mod=modPolyester)
  }

>>>>

    # randomly sample a log2FC from truncated N(0,0.5) (greater than 0.5) 
    log2FC <- rep(0, nrow(counts))
    # log2FC[DE] <- rtruncnorm(nDE, 1, sd=.5) * sample(c(1,-1), size=nDE, replace=TRUE)
    log2FC[DE] <- c(rnorm(nDE, sd = 1), rep(0,nrow(counts)-nDE))
    dat_alt = create_read_numbers(paramPolyester$mu, paramPolyester$fit,
                                  paramPolyester$p0, m=dim(counts)[1], 
                                  n=sampleSize*2, beta=cbind(log2FC), 
                                  mod=modPolyester)
  }
